% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Owen Lynch}
\address{(617) 279-3222, root@owenlynch.org}

 
\begin{resume}
 
\section{EDUCATION} Brown University \\
                Pursuing BSc. Mathematics, May 2020 \\
 
\section{PROJECTS} {\sl HackMIT 2017 ``Pathways''} \\
                Simulation of traffic routing algorithm to evacuate natural disasters. Won ``Hack with Most Startup Potential,'' ``Best Use of Location Data,'' and ``Moonshot.'' Written in Python using Networkx and Pygame \\
                {\sl Interactive Graph Editor} \\
                   Keyboard driven extensible graph editor, purpose is to explore nonlinear syntax for programming language design. Written in Haskell using Cairo. \\
                {\sl Not Gonna Happen} \\
                Metronome that tracks your progress in a graphical calendar: if you don't practice every day it's not gonna happen! Written in Haskell using Yesod and Diagrams.
 
\section{EXPERIENCE}
                {\sl Software Intern} \hfill 2018 \\
                Tesla Motors \\
                Worked on internal car network systems using Haskell. \\
                {\sl Student Researcher} \hfill (2016-2017) \\
                New England Complex Systems Institute \\
                Researched and implemented novel techniques in image processing. Wrote large-scale data scraping infrastructure. Helped to migrate large amounts of data. Studied novel information theoretic methods for modeling changes in complex systems. Worked in Python, R, and C. \\
 
                {\sl Math Resource Center Tutor} \hfill            (2017) \\
                Brown University \\
                Tutored Brown students in calculus (up through multivariable) and linea algebra. \\

                {\sl Math Classroom Assistant} \hfill        (2014) \\
                Winter Hill Community School \\
                Helped run a summer math class for struggling sixth to eighth grad students. \\

                {\sl Web Developer Intern} \hfill (2013) \\
                Green Streets Initiative \\
                Wrote live-updating leaderboard for Walk-Ride day competition. Implemented Django and Postgresql backnd and JQuery frontend, and administered Debian server. \\

\section{TECHNICAL \\ SKILLS} Haskell, C, Python, Rust, MATLAB, Linux
 
\section{MISC.} I play violin, swing and blues dance, and rockclimb.

\end{resume}
\end{document}







